Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-04 manuscript.Rmd

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

@@

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = med_incomeE)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = blackE)) +
	theme_map +
	scale_fill_viridis_c()

>>>>

```{r join_sf}
centroids <- data.frame(cbind(st_coordinates(st_centroid(dc_acs_tracts))))

centroids <- centroids %>%
  mutate(GEOID = dc_acs_tracts$GEOID)

dc_acs_tracts <- left_join(x = dc_acs_tracts, y = centroids, by = "GEOID")

travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

@@

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = med_incomeE)) +
	theme_map +
	scale_fill_viridis_c()
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = blackE)) +
	theme_map +
	scale_fill_viridis_c()
